spinifex: An R Package for Creating a Manual Tour of Low-dimensional Projections of Multivariate Data

### 2020-09-12 spinifex_RJpostProofing_20200912/spyrison-cook.tex
and associated zips

@@

\caption{\label{tab:functionsTable}Summary of available functions.}
\centering
\begin{tabular}[t]{lll}
\toprule
Type & Function & Description\\
\midrule
construction & create\_manip\_space & forms the 3D space of rotation\\
construction & rotate\_manip\_space & performs 3D rotation\\
construction & manual\_tour & generates sequence of 2D frames\\
 &  & \\
render & array2df & turn the tour path array into long form, for plotting\\
render & render\_ & render long form as a ggplot2 objection for animation\\
render & render\_plotly & render the animation as a plotly object (default)\\
render & render\_gganimate & render the animation as a gganimate object\\
 &  & \\
animation & play\_tour\_path & composite function animating the specified tour path\\
animation & play\_manual\_tour & composite function animating the specified manual tour\\
 &  & \\
specialty & print\_manip\_space & table of the rotated basis and manip space\\
specialty & view\_frame & display the reference axes of a given basis\\
specialty & view\_manip\_space & illustrative display of any manip space\\
\bottomrule
\end{tabular}
\end{table}

@@

The function \texttt{view\_frame} can be used to show a projection of
the basis, or with the data overlaid. For example, the plots in Figures
\ref{fig:step0} and \ref{fig:step3} were made with code similar to this:

\begin{Schunk}
\begin{Sinput}
## View a basis and projected data 
view_frame(basis = f_basis, 
              data = f_data,
              color = f_clas,
              shape = f_clas)
\end{Sinput}
\end{Schunk}

>>>>

\begin{Schunk}
\begin{Soutput}
#> function (`_class` = NULL, `_inherit` = NULL, ...) 
#> {
#>     e <- new.env(parent = emptyenv())
#>     members <- list(...)
#>     if (length(members) != sum(nzchar(names(members)))) {
#>         abort("All members of a ggproto object must be named.")
#>     }
#>     if (length(members) > 0) {
#>         list2env(members, envir = e)
#>     }
#>     `_inherit` <- substitute(`_inherit`)
#>     env <- parent.frame()
#>     find_super <- function() {
#>         eval(`_inherit`, env, NULL)
#>     }
#>     super <- find_super()
#>     if (!is.null(super)) {
#>         if (!is.ggproto(super)) {
#>             abort("`_inherit` must be a ggproto object.")
#>         }
#>         e$super <- find_super
#>         class(e) <- c(`_class`, class(super))
#>     }
#>     else {
#>         class(e) <- c(`_class`, "ggproto", "gg")
#>     }
#>     e
#> }
#> <bytecode: 0x000000001d298b08>
#> <environment: namespace:ggplot2>
\end{Soutput}
\begin{figure}

@@

\caption{\label{tab:functionsTable}Summary of available functions.}
\centering
\begin{tabular}[t]{lll}
\toprule
Type & Function & Description\\
\midrule
construction & create\_manip\_space & forms the 3D space of rotation\\
construction & rotate\_manip\_space & performs 3D rotation\\
construction & manual\_tour & generates sequence of 2D frames\\
 &  & \\
render & array2df & turn the tour path array into long form, for plotting\\
render & render\_ & render long form as a ggplot2 objection for animation\\
render & render\_plotly & render the animation as a plotly object (default)\\
render & render\_gganimate & render the animation as a gganimate object\\
 &  & \\
animation & play\_tour\_path & composite function animating the specified tour path\\
animation & play\_manual\_tour & composite function animating the specified manual tour\\
 &  & \\
specialty & print\_manip\_space & table of the rotated basis and manip space\\
specialty & oblique\_frame & display the reference axes of a given basis\\
specialty & view\_manip\_space & illustrative display of any manip space\\
\bottomrule
\end{tabular}
\end{table}

@@

The function \texttt{oblique\_frame} can be used to show a projection of
the basis, or with the data overlaid. For example, the plots in Figures
\ref{fig:step0} and \ref{fig:step3} were made with code similar to this:

\begin{Schunk}
\begin{Sinput}
## View a basis and projected data 
oblique_frame(basis = f_basis, 
              data = f_data,
              color = f_clas,
              shape = f_clas)
\end{Sinput}
\end{Schunk}
